\section{Datasheet for the Synthetic Stream}\label{app:datasheet}

Following \citet{gebru2021datasheets}. The bench emits a fresh datasheet per
stream; the fields below describe the streams used in this paper (the
distractor-heavy primary regime; other regimes differ only in label mix).

\paragraph{Motivation.} The dataset is a \emph{synthetic continual task stream}
created to measure the quality of memory consolidation against known
ground-truth relevance --- the only substrate on which pruning precision/recall
is directly measurable and confounds are controllable. It was created by the
Slow Wave project for this study; no external funding or third party is involved.

\paragraph{Composition.} Each instance is either a \emph{task} or an
\emph{ingest item}. Every item carries exactly one ground-truth relevance label
$\in\{\texttt{signal},\texttt{distractor},\texttt{noise}\}$. \texttt{signal}
items are $(\text{subject},\text{attribute},\text{value})$ facts that answer
probe queries; \texttt{distractor} items are plausible but mission-irrelevant
facts drawn from a separate namespace; \texttt{noise} items are random tokens
with no fact. A stream has $n\_\text{tasks}=5$ tasks of
$\text{items\_per\_task}=40$ items (200 items) in the primary configuration,
with $8$ subjects/task, $4$ attributes, $12$ values, a distractor namespace of
$64$, and a noise vocabulary of $128$. The label mix for the primary
(distractor-heavy) regime is signal $0.34$ / distractor $0.40$ / noise $0.26$.
A held-out probe set ($6$ probes/task) is decoupled from the online stream. The
dataset is self-contained and synthetic; it contains no personal, sensitive, or
confidential data (Non-Goal NG5).

\paragraph{Collection / generation process.} Items are generated procedurally
and are \emph{byte-deterministic given a stream seed}: the same seed yields a
byte-identical stream and datasheet. Temporal structure (recency bias, drift)
and contradiction rate are configurable (all $0$ in the primary configuration).
Each stream is tagged with exactly one continual-learning scenario
(here \texttt{task-incremental}; \citealp{vandeven2022threetypes}); no
cross-scenario mixing is permitted.

\paragraph{Labeling and the confound guard.} Ground-truth relevance labels are
assigned at generation time and stored in an \emph{offline-only} label sidecar.
A confound guard (functional requirement FR1.6) enforces --- in code, asserted
by test, and checked by an import firewall --- that these labels are unreachable
from any online retrieval or priority code path, preventing an oracle-replay
leak. Only offline scoring may read them.

\paragraph{Uses.} The stream supports continual-learning evaluation (the
accuracy matrix $R[i,j]$), mechanism-level prune-quality scoring (precision /
recall / F1 of discarding distractors vs.\ retaining signal), and cost/footprint
measurement. It is \emph{not} intended as a natural-language benchmark and makes
no claim of external validity to natural data.

\paragraph{Distribution and maintenance.} The generator, configs, and the
committed run manifests ship with the repository; any stream is regenerable from
its seed and config. The datasheet emitter is versioned with the codebase; the
authoritative interface is documented in the repository's Phase~1 contract.
