\section{Model Card}\label{app:modelcard}

Following \citet{mitchell2019modelcards}. This card covers the two models the
bench uses: the (frozen) reasoning/summarisation LLM and the local embedding
model.

\paragraph{Model details.} The configured reasoning and dream-summarisation
model is \texttt{\SWmodelID} (a pinned Claude snapshot), called with sampling
temperature $0.0$, \texttt{max\_tokens}~$=64$, \texttt{top\_p} unset, and
\texttt{effort} unset. \textbf{The runs in this paper used a deterministic mock
LLM} (\texttt{mocked}=\SWmodelMocked), because no \texttt{ANTHROPIC\_API\_KEY}
was present on the run machine: the mock returns text fully determined by
$(\text{model id},\text{system},\text{prompt})$, so the pipeline is
byte-reproducible. Consequently every number is a \emph{mechanism demonstration},
not a measurement of the real snapshot (Section~\ref{sec:limitations}). The
local embedding model is a hash bag-of-words backend (\texttt{hash-bow-v1},
dimension $384$, version $1.0$); it is deterministic given its input and
CPU-friendly. (A \texttt{sentence-transformers} backend such as
\texttt{bge-small-en-v1.5} is supported as a configuration option but was not
used for these committed runs.)

\paragraph{Intended use.} The models are a measurement vehicle for studying
external-memory consolidation around a \emph{frozen-weights} agent. Intended use
is research on the bench's synthetic stream. Out-of-scope: production deployment,
any use requiring biological fidelity, and any efficacy claim beyond the tested
synthetic, mock-LLM regime.

\paragraph{Factors and metrics.} Relevant factors are the distractor regime,
the stream/sampling seed, and the dream-operator configuration. Metrics are the
continual-learning set (ACC, BWT, FWT, per-task forgetting;
\citealp{lopezpaz2017gem,chaudhry2018riemannian}), the mechanism-level prune
precision/recall/F1 and decay-vs-relevance calibration, cost (tokens, memory
vectors/bytes, p95 latency, wall-clock, sim-time compression), generator
fidelity/drift, and the TMR-style retention lift.

\paragraph{Training data.} \textbf{None: weights are frozen.} No fine-tuning,
RLHF, or retraining is performed; ``consolidation'' acts only on the external
memory. The local embedder is not trained by this project.

\paragraph{Ethical considerations and caveats.} The synthetic stream contains no
personal or sensitive content (NG5). The dominant caveat is the mock-LLM regime
(above). For any real-model run, the standing caveats are LLM nondeterminism even
at temperature~0, eventual snapshot deprecation, and summarisation drift; the
bench mitigates these with a pinned model id, multi-seed dispersion, a
temperature-0 stability control, a memory-drift detector, and archived
transcripts, rather than assuming reproducibility.
