\section{Reproducibility Appendix}\label{app:repro}

This appendix gives the information requested by the NeurIPS reproducibility
checklist \citep{pineau2021reproducibility}: the pinned model, the full
hyperparameters and swept grids, the prompts, the per-run manifest schema, and
the one-command reproduction.

\paragraph{Pinned model and environment.} Reasoning/summarisation model
\texttt{\SWmodelID} (pinned snapshot), sampling temperature $0.0$,
\texttt{max\_tokens}~$=64$; runs executed under the deterministic mock LLM
(\texttt{mocked}=\SWmodelMocked). Local embedder \texttt{hash-bow-v1}, dimension
$384$. Python $3.12$; package version $0.1.0$; statistics implemented in pure
NumPy. Committed result at git \texttt{\SWgitCommit}.

\paragraph{Hyperparameters, search ranges, and prompts.} Given in full in
Appendix~\ref{app:hyper} (stream, memory, dream-engine, and evaluation
hyperparameters; the three swept grids; and the transfer / augment / reasoning
prompts).

\paragraph{Per-run manifest schema (FR6.1).} Every run writes a JSON manifest
whose top-level keys are: \texttt{manifest\_version}, \texttt{experiment},
\texttt{run\_id}, \texttt{config\_hash}, \texttt{created\_at};
\texttt{model} (\texttt{id}, \texttt{mocked}, and \texttt{sampling}:
\texttt{temperature}/\texttt{max\_tokens}/\texttt{top\_p}/\texttt{effort});
\texttt{llm} (\texttt{model\_id}, \texttt{mocked}, token counts, output
\texttt{text\_sha256});
\texttt{embedding} (\texttt{backend}, \texttt{model}, \texttt{version},
\texttt{dim});
\texttt{seeds} (master + per-arm derivation) and \texttt{seed\_list};
\texttt{hyperparameters} and \texttt{search\_ranges};
\texttt{cost} (\texttt{api\_calls}, \texttt{tokens}.\{input,output,total\},
\texttt{wall\_clock\_s}, and per-arm memory vectors/bytes, retrieval calls, and
p95 latency in the results block);
\texttt{git} (\texttt{commit}, \texttt{branch}, \texttt{dirty});
\texttt{sim\_time} (\texttt{compression\_factor});
\texttt{platform}, \texttt{python\_version}, \texttt{package\_version};
\texttt{results} (the full per-(arm,seed) experiment: $R[i,j]$, continual
metrics, prune quality, calibration, footprint, statistics, A/A, prereg primary
endpoint, drift, stability); and
\texttt{nondeterministic\_fields}, which explicitly lists the fields that may
vary under a real LLM --- \texttt{created\_at}, \texttt{cost.wall\_clock\_s},
output token counts, \texttt{llm.text\_sha256}/\texttt{text\_preview}, the git
fields, and per-step latencies --- so a reader knows exactly which values are not
byte-stable. (Under the mock LLM even most of these are stable run-to-run; the
field merely marks what is \emph{permitted} to vary.)

\paragraph{One-command reproduction.} From a clean checkout with the package
installed (\texttt{pip install -e ".[viz]"}):
\begin{itemize}
  \item \textbf{Headline figures} (the EC2 one-command regeneration from the
  committed result): \texttt{make repro-figures}, i.e.\
  \texttt{python -m slow\_wave.paper.figures --result phase5/phase5\_result.json
  --out paper/figures}.
  \item \textbf{In-text numbers and the per-arm table}:
  \texttt{make repro-numbers}, i.e.\
  \texttt{python -m slow\_wave.paper.numbers --result phase5/phase5\_result.json
  --out paper/generated} (the manuscript \texttt{\textbackslash input}s these, so
  no number is hand-transcribed).
  \item \textbf{Full grid + analysis + figures}: \texttt{make repro-phase5}.
  \item \textbf{The entire manuscript} (numbers + figures + PDF):
  \texttt{make repro-paper} (\texttt{scripts/build\_paper.sh}).
\end{itemize}
Because the grid runs under the deterministic mock LLM when no API key is
present, every non-LLM artifact is byte-reproducible across runs with the same
config and seeds; the \texttt{nondeterministic\_fields} list flags everything
that is not. This is a mechanism-demonstration reproduction
(Section~\ref{sec:limitations}); a real-model run is reproducible only up to LLM
nondeterminism, which is why the bench reports dispersion, a temperature-0
stability control, and a memory-drift detector rather than assuming
bit-for-bit determinism.
