\section{Introduction}\label{sec:intro}

As persistent ``second-brain'' agents proliferate, continuous ingestion swamps
working memory with material that never improves mission performance. The
dominant engineering response is to enlarge the context window or to stuff
every trace into a retrieval store, but both strategies scale cost with history
rather than with relevance. Biology solved an analogous problem with
\emph{sleep}. Consolidation is not one process but a coordinated sequence:
replay of recent experience through hippocampal sharp-wave ripples
\citep{buzsaki1989twostage,buzsaki2015ripples}, systems-level transfer from
hippocampus to neocortex \citep{mcclelland1995cls,klinzing2019systems}, and a
synaptic downscaling that renormalises strength while protecting what was
replayed \citep{tononi2006shy,tononi2014price}. A complementary view holds that
sleep also actively \emph{forgets} \citep{crick1983dreamsleep,poe2017forgetting}
and that dreaming aids generalisation \citep{hoel2021overfitted}.

The central scientific bet of this project is that an \emph{engineered analogue}
of this cycle improves long-horizon agent performance and memory efficiency.
Crucially, we study this for \textbf{frozen-weights} LLM agents --- the
realistic deployment regime, in which the model is fixed and only the external
\emph{memory} is consolidated. We do not fine-tune, do RLHF, or train new
models; the question is whether \emph{memory} consolidation alone, decomposed
into biologically-motivated mechanisms, can carry an effect. We frame
neuroscience strictly as a source of testable mechanisms and metaphors, never
as evidence of efficacy, and we make no claim that the bench models the brain.

To test the bet falsifiably we built \textbf{Slow Wave}, a test bench rather
than a demo. Its distinguishing feature is a synthetic continual task stream
carrying \emph{ground-truth relevance labels} (\texttt{signal} /
\texttt{distractor} / \texttt{noise}) that are visible to offline scoring only,
never to the online retrieval or priority path. This single design choice
unlocks something neither neuroscience nor existing LLM-memory benchmarks can
measure: the \emph{quality} of consolidation --- the precision and recall with
which a mechanism discards distractors while retaining signal --- reported
\emph{decoupled} from downstream task accuracy, since the two can diverge.

We then ask the question the way a skeptic would. The treatment (a full
four-operator dream cycle) is compared against a battery of \SWnArms{} control
arms through a matched-budget controller over LLM-token, retrieval, and memory
budgets (with an accuracy-vs-compute Pareto frontier reported where budgets
cannot be matched within tolerance, as they cannot for the full cycle here), with
a single \emph{preregistered} primary endpoint, a ground-truth-blind
random-pruning negative control, an oracle prune ceiling, a long-context baseline
(the key validity threat), a deployable shallow-synthesis control, and an A/A
control that fixes the noise floor any claimed effect must clear. The verdict is recorded whichever way the data fall, and a
negative or cost-unfavourable result is a first-class, pre-specified outcome.

\paragraph{An honesty caveat, stated up front.} The numbers in this paper were
produced under a \emph{deterministic mock LLM} (no live model key was present on
the run machine), so the whole experiment is byte-reproducible. Consequently
every quantitative result here is a \textbf{mechanism demonstration in the
synthetic, mock-LLM regime} --- a statement about whether the apparatus and its
operators behave as designed --- and \emph{not} a scientific claim about a real
Claude model. We restate this caveat wherever results appear
(Section~\ref{sec:limitations}).

\paragraph{Contributions.} Concretely, this work contributes:
\begin{itemize}
  \item \textbf{An apparatus.} An instrumented, reproducible, \emph{mechanism-decomposed}
  continual-learning bench for LLM-agent memory: a labelled synthetic stream
  with controllable distractor regimes and an enforced confound guard (relevance
  labels are unreachable from any online code path), a physically dual-store
  memory substrate (episodic / semantic / auditable archival, with salience,
  provenance, and write-protection), and a four-operator dream engine
  (\emph{replay}, \emph{transfer}, \emph{downscale}, \emph{generative-augment})
  whose operators are independently ablatable in a two-phase (NREM\,$\to$\,REM)
  cycle.
  \item \textbf{A protocol.} A preregistered, budget-controlled experimental design
  with a \SWnArms{}-arm control battery (including a ground-truth-blind negative
  control, an oracle ceiling, a long-context baseline, and an A/A noise floor),
  a metric suite that reports continual-learning metrics (ACC/BWT/FWT/forgetting)
  \emph{and} mechanism-level prune precision/recall/F1 against ground-truth
  relevance, and a statistics suite with bootstrap CIs, robust aggregates,
  paired and omnibus tests, effect sizes, and multiple-comparison correction.
  \item \textbf{Ablation results, including negatives.} Under the mock-LLM
  mechanism-demonstration regime: a confirmed improvement of the full dream cycle
  over the no-sleep baseline on the preregistered primary endpoint
  ($\Delta=\SWprimaryDiff$), with the registered secondary contrast confirming it
  also beats the replay-only re-exposure control --- the mechanism question H1 was
  written to answer, \emph{not} a claim that the cycle is the best deployable arm,
  and realised at higher token and memory cost, so the contrast is reported on the
  accuracy-vs-compute Pareto frontier; a replay-targeting effect that demonstrably
  moves signal into durable memory (its standardised size against a
  targeted-memory-reactivation benchmark is reported but treated as a determinism
  artifact, not a favourable comparison); \emph{and}, reported with equal weight,
  two cost-unfavourable findings --- that an uncapped long-context baseline
  dominates on raw accuracy at maximum memory cost with \emph{no} cost-adjusted crossover
  in the swept stream lengths, and that a simpler deployable shallow-synthesis
  control (\texttt{reflection}) attains higher final accuracy than the full cycle
  at lower token cost (Table~\ref{tab:arms}), leaving the cycle off the
  accuracy-vs-token Pareto frontier --- together mapping the cost regime in which
  external consolidation, and this particular four-operator cycle, is and is not
  worth paying for.
\end{itemize}
