\section{Test-Bench Design}\label{sec:design}

Slow Wave is organised as an experiment harness that drives a wake agent, a
dream engine, and a dual-store memory substrate over a synthetic stream, writing
a self-describing manifest for every run. We summarise each component; full
hyperparameters, prompts, and the manifest schema are in
Appendices~\ref{app:hyper} and~\ref{app:repro}.

\paragraph{Synthetic continual task stream.} The generator emits a long, ordered
stream of tasks and ingest items, each carrying exactly one \emph{ground-truth
relevance label} --- \texttt{signal} (mission-relevant), \texttt{distractor}
(plausible but irrelevant), or \texttt{noise} (random). Distractor regimes
(e.g.\ signal-rich, balanced, distractor-heavy), temporal structure, and
explicit \emph{contradictions} (items that conflict with earlier signal) are
controllable, and the stream is byte-deterministic given a seed. Each stream is
tagged with exactly one continual-learning scenario
\citep{vandeven2022threetypes}, and ships a Gebru-style datasheet
(Appendix~\ref{app:datasheet}; \citealp{gebru2021datasheets}) and a held-out
probe set that decouples evaluation from the online stream and yields the
accuracy matrix $R[i,j]$ (accuracy on task $j$ after learning through task $i$).
The decisive design rule is a \emph{confound guard}: ground-truth labels are
available to offline scoring only and are statically unreachable from any online
retrieval or priority code path, preventing an ``oracle-replay'' leak. This is
enforced in code and asserted by test.

\paragraph{Dual-store memory substrate.} Following CLS
\citep{kumaran2016cls,mcclelland1995cls}, memory is physically split into a fast,
append-only \textbf{episodic} buffer (timestamped raw wake traces, locally
embedded) and a slow, compressed \textbf{semantic} store, plus an auditable
\textbf{archival} tier. Each item carries a salience weight and metadata
(recency, access count, novelty as embedding distance to consolidated memory,
surprise, and a provenance pointer to source episodes). Retrieval is the
recency\,$\times$\,importance\,$\times$\,relevance policy of
\citet{park2023generativeagents}. Forgetting \emph{demotes} items to the
archival tier rather than hard-deleting, so eviction is auditable and reversible;
and consolidated high-importance memories carry an EWC-spirit write-protection
flag \citep{kirkpatrick2017ewc}, so a later distractor silently overwriting a
protected fact is a logged failure event.

\paragraph{Wake agent.} The wake loop ingests stream items, attempts tasks,
appends episodic traces, retrieves from memory, and calls the LLM for reasoning.
No semantic-store writes occur during wake --- writes are gated to scheduled
sleep windows --- so the no-sleep configuration is a genuine
catastrophic-forgetting reference. The agent emits, per task, the data to
populate $R[i,j]$ plus token, compute, and latency telemetry, and self-moderates
against a token budget that the harness also enforces as a ceiling.

\paragraph{The dream engine: four ablatable operators.} The engine runs a
two-phase (NREM-like\,$\to$\,REM-like) cycle, with each operator an independent
config toggle:
\begin{itemize}
  \item \textbf{Replay} re-samples, re-embeds, and re-scores a subset of recent
  episodics in compressed batches. Sampling is \emph{uniform} (the DQN baseline;
  \citealp{mnih2015dqn}) or \emph{prioritized} by
  recency\,$\times$\,relevance\,$\times$\,novelty\,$\times$\,surprise, with
  importance-sampling weights logged \citep{schaul2016per}.
  \item \textbf{Transfer} uses LLM ``dream'' summarisation to distill sampled
  episodics into durable semantic entries (episodic\,$\to$\,semantic promotion),
  enforcing CLS \emph{interleaving} (each batch mixes new episodes with sampled
  prior consolidated memories); removing interleaving is the on-purpose
  catastrophic-interference condition. Provenance is preserved.
  \item \textbf{Downscale} multiplies every item's salience by a factor below one
  (global renormalisation, the SHY analogue;
  \citealp{tononi2006shy,tononi2014price}), then re-potentiates only replayed
  items --- ``decay all, protect signal.'' The decay function is swappable among
  exponential, Weibull, and ACT-R activation decay.
  \item \textbf{Generative-augment} (REM-like) synthesises paraphrases,
  counterfactuals, and abstractions (pseudo-episodes) from episodics, the LLM
  analogue of generative replay \citep{shin2017generativereplay} and world-model
  imagination \citep{ha2018worldmodels}; generator fidelity/drift is tracked per
  cycle.
\end{itemize}
Semantic writes occur \emph{only} inside scheduled sleep windows (gating; a
``continuous online writes'' comparison condition exists), a sleep-pressure
controller can scale cycle frequency and downscaling magnitude to accumulated
wake churn, and an optional conflict/unlearning step demotes (never destroys)
contradictions in the Crick--Mitchison spirit \citep{crick1983dreamsleep}.

\paragraph{Reproducibility substrate.} Every run emits a JSON manifest recording
the exact model id and sampling params, embedding model/version/dimension, all
hyperparameters and search ranges, the seed list, the git commit hash,
wall-clock and token/compute cost, and the sim-time compression factor; figures
and numbers are regenerated from these manifests by committed scripts
(Section~\ref{sec:repro}, Appendix~\ref{app:repro}).
