\section{Experimental Protocol}\label{sec:protocol}

\paragraph{Preregistration.} Before the experiment grid was run, a
registered-report-style artifact was committed to version control naming the
hypotheses, the single primary endpoint, the seed plan and power analysis, the
statistical tests, and explicit rejection criteria (Appendix~\ref{app:repro};
\citealp{pineau2021reproducibility}). The analysis code reads the preregistered
primary endpoint and refuses to compute any other, so falsifiability is visible
in the code. The hypotheses are: \textbf{H1} --- at matched LLM-token,
retrieval, and memory budgets, the full four-operator dream cycle
(\texttt{full\_dream}) yields higher final average accuracy (ACC) than the
no-sleep baseline (\texttt{no\_sleep}) on a distractor-heavy stream, with the
paired per-seed difference strictly positive and its bootstrap 95\% CI excluding
zero; \textbf{H0} --- no such improvement, or an effect not exceeding the A/A
noise floor. The \textbf{primary endpoint} is
\texttt{\SWprimaryEndpoint}: the paired (by seed) difference in final ACC between
\texttt{full\_dream} and \texttt{no\_sleep}, aggregated as the mean paired
difference, with a bootstrap 95\% CI, a paired Wilcoxon signed-rank test, and a
standardised effect size; the effect must also exceed the A/A noise floor to
count as confirmed.

\paragraph{Control battery.} \SWnArms{} arms share one harness at matched
budgets: \texttt{no\_sleep} (wake-only baseline), \texttt{replay\_only},
\texttt{downscale\_only}, \texttt{random\_pruning} (a ground-truth-blind negative
control), \texttt{full\_dream} (treatment), \texttt{reflection} (the
shallow-synthesis control of \citealp{park2023generativeagents}), \texttt{oracle}
(prune exactly the injected distractors using the held-out labels --- a ceiling,
not a deployable arm), \texttt{long\_context} (the entire stream stuffed into a
long context with no consolidation --- the key validity threat), and \texttt{aa}
(two identical configs differing only in seed --- the noise floor any claimed
effect must exceed). A matched-budget controller equalises LLM tokens, retrieval
calls, and final memory-vector count across arms within tolerance and records
the actuals; where matching is impossible we report an accuracy-vs-compute
Pareto frontier instead of a single matched point.

\paragraph{Metrics.} From $R[i,j]$ we compute average accuracy, backward and
forward transfer \citep{lopezpaz2017gem}, and the per-task Forgetting Measure
\citep{chaudhry2018riemannian}. The bench's distinctive measurement is
\emph{mechanism-level}: precision, recall, and F1 of consolidation at discarding
distractors versus retaining signal, plus a calibration curve of embedding-decay
against true relevance --- reported \emph{decoupled} from downstream accuracy.
We also record cost (memory footprint in vectors and bytes, test-time tokens,
p95 latency, wall-clock, and sim-time compression factor;
\citealp{diazrodriguez2018metrics}), generator fidelity/drift of dream
summaries, and a TMR-style retention lift for the force-replayed labelled subset
benchmarked against the meta-analytic $g\approx\SWtmrBench$ of
\citet{hu2020tmr}.

\paragraph{Statistics.} We vary both the stream-generation seed and the
agent/LLM sampling seed, with $n=\SWnSeeds$ seeds per arm (floor of
\SWpowerFloor; \citealp{colas2018seeds}). We report stratified bootstrap 95\%
CIs and \texttt{rliable} robust aggregates (IQM, performance profiles,
probability of improvement; \citealp{agarwal2021rliable}); paired Wilcoxon
signed-rank tests for arm-vs-baseline contrasts and a Friedman omnibus with
post-hoc comparisons for the multi-arm family \citep{demsar2006statistical};
standardised effect sizes with CIs; and Holm--Bonferroni multiple-comparison
correction across the arm-vs-control family. The statistics layer is implemented
in pure NumPy so the pipeline reproduces without heavyweight dependencies.

\paragraph{Bias controls.} Metric computation is blind (labels are offline
only). LLM nondeterminism is mitigated by a pinned model id, multi-seed
dispersion, and a temperature-0 \emph{stability} control that quantifies
run-to-run variance of the dream summariser; a \emph{memory-drift} detector
flags when repeated summarisation degrades rather than distills memory. The A/A
control fixes the noise floor.

\paragraph{Grid, length sweep, and sim-vs-real.} The full grid spans the
\SWnArms{} arms $\times$ \SWnRegimes{} distractor regimes $\times$ \SWnSeeds{}
seeds (\SWnCells{} cells; \SWnDropped{} dropped, logged with no silent caps). A
separate \emph{stream-length sweep} over $L\in\{\SWcrossoverLengths\}$ probes the
long-context crossover, and a \emph{sim-vs-real} comparison runs each key arm at
an accelerated high-compression setting (\SWsimNtasksSim{} tasks, compression
$\approx\SWsimCompression\times$) and at a real low-compression long-horizon
setting (\SWsimNtasksReal{} tasks) to test whether time-compression distorts
retention curves.

\paragraph{Regime of these results.} The grid was executed under a
\emph{deterministic mock LLM} (no live model key on the run machine). This makes
every artifact byte-reproducible but means the results are a \textbf{mechanism
demonstration in the synthetic, mock-LLM regime}, not a measurement of a real
Claude model. We carry this caveat into every result
(Sections~\ref{sec:results},~\ref{sec:limitations}).
