\section{Limitations}\label{sec:limitations}

We state the threats to validity plainly; several bound the claims sharply.

\paragraph{Mock-LLM regime (the dominant caveat).} Every quantitative result in
this paper was produced under a \emph{deterministic mock LLM}, because no live
model key was present on the run machine. This is a deliberate honesty-by-design
choice --- it makes the entire grid byte-reproducible --- but it means the
results are a \textbf{mechanism demonstration in the synthetic, mock-LLM regime}:
they show that the apparatus, its operators, its metrics, and its statistics
behave as designed, and nothing more. They are \emph{not} measurements of a real
Claude model. In particular, the very large primary effect ($d=\SWprimaryD$) and
the near-zero dispersion of the stability control are artifacts of a noiseless
mock summariser; a real model would introduce sampling variance, summarisation
drift, and refusals that the mock cannot. The same noiseless determinism inflates
\emph{any} standardised effect computed here --- including the TMR-style Hedges'
$g=\SWtmrG$ --- so its apparent margin over the $g\approx\SWtmrBench$ benchmark
reflects an engineered operator scored against noisy human data, not evidence of a
strong targeting effect; the direction of the lift, not its benchmark-relative
magnitude, is what the mock can speak to. For the same reason, the inferential
layer --- bootstrap CIs, the paired Wilcoxon and Friedman tests, Holm--Bonferroni
correction, and the \texttt{rliable} robust aggregates --- characterises dispersion
across seed-driven stream re-instantiations rather than population-level inference,
and the signed-rank $p$ is computed by a normal approximation that is
near-saturated at $n=\SWnSeeds$ seeds; we report these as descriptive statistics
and treat genuine hypothesis testing, ideally with an exact signed-rank test, as
pending a real-model run. No efficacy claim about a real model should be read into
any number here.

\paragraph{What the accuracy scores measure (retention, not probe-time reasoning).}
Under the mock LLM, probe answers are read by exact-key lookup over active memory
and never from the model (Appendix~\ref{app:hyper}). Final accuracy is therefore a
deterministic function of \emph{which facts survive in active memory}: the
consolidation operators move ACC only by changing what is retained, and the frozen
LLM does no probe-time reasoning that affects any score. The continual-learning
metrics (ACC/BWT/FWT) remain valid \emph{retention} measures --- they quantify
whether replayed signal survives episodic eviction, exactly what consolidation is
meant to affect --- but in this regime they are not measurements of model
reasoning. A direct consequence is that \texttt{long\_context}'s perfect accuracy
(Table~\ref{tab:arms}) and the resulting absence of a long-context crossover
(Section~\ref{sec:results}) are structurally entailed by exact-key retention rather
than empirical findings about long-context reasoning; a real model would face
token cost growing with stream length and lost-in-the-middle degradation that the
lookup cannot show.

\paragraph{Unmatched budgets (the primary contrast is a cost-effectiveness result).}
The matched-budget controller is part of the apparatus, but in this grid it does
\emph{not} succeed: \texttt{full\_dream} spends more LLM tokens and holds more
memory vectors than \texttt{no\_sleep} (Table~\ref{tab:arms}), outside the
controller's tolerance band, so the committed \texttt{budget\_matched} verdict is
false in every regime. Per the preregistered fallback we therefore report the
primary contrast on the accuracy-vs-compute Pareto frontier: the full dream cycle
buys $\Delta=\SWprimaryDiff$ final ACC over the no-sleep baseline at a higher token
and memory price, not for free at a matched budget. The defensible claim is
cost-effectiveness on this frontier, not a budget-neutral win.

\paragraph{The treatment is not the cost-optimal deployable arm.} On the
accuracy-versus-token frontier the full four-operator cycle is Pareto-dominated not
only by the uncapped \texttt{long\_context} ceiling but by \texttt{reflection}, a
deployable shallow-synthesis control \citep{park2023generativeagents} that reaches
higher final accuracy at lower token cost and comparable memory
(Table~\ref{tab:arms}, Figure~\ref{fig:pareto}). The preregistered H1 asked only
whether the full cycle beats its no-sleep/replay-only ablations --- the mechanism
question --- which it does; it did \emph{not} ask, and these results do not show,
that the full cycle is the best deployable consolidation strategy. Its
distinguishing value here is operator-level decomposability and the
consolidation-quality readout (on which it retains higher recall and F1 than
\texttt{reflection}), not a superior accuracy-per-token operating point.

\paragraph{Frozen-weights scope.} We study \emph{memory} consolidation for
\textbf{frozen-weights} agents: the model is never fine-tuned, RLHF'd, or
retrained, and ``consolidation'' refers entirely to operations on an external
memory. Findings therefore say nothing about weight-level continual learning,
and the EWC-spirit protection here is a memory-write flag, not a parameter
penalty.

\paragraph{Sim-time-compression validity.} Most runs use accelerated ``sim-time''
cycles for cheap iteration, validated against a few real low-compression
long-horizon runs. We report the sim-vs-real agreement explicitly
(Section~\ref{sec:results}): the ranking is preserved here (Spearman
$\SWsimSpearman$), but the maximum absolute mean-ACC divergence is
$\SWsimMaxDiv$, which is not negligible. A documented inversion at larger scale
would be a finding, not a bug; we have not swept far enough to exclude one.

\paragraph{Proprietary-model reproducibility.} Real runs would depend on a
proprietary model behind an API. LLM calls are nondeterministic even at
temperature~0, pinned snapshots are eventually deprecated, and exact transcripts
cannot be guaranteed reproducible across snapshots. We mitigate (pinned model
id, multi-seed dispersion, a temperature-0 stability control, archived
transcripts) rather than assume reproducibility, but the caveat is real for any
non-mock run.

\paragraph{Scenario and domain scope.} Results are confined to a single
synthetic, task-incremental stream; each stream is tagged with exactly one
continual-learning scenario and we perform \emph{no} cross-scenario aggregation
\citep{vandeven2022threetypes}. We do not run a secondary ``second-brain'' domain
in this version, and the long-context comparison was swept only over
$L\in\{\SWcrossoverLengths\}$ --- so the absence of a crossover is a statement
about that range, not a universal claim. External validity to natural data,
other scenarios, and longer streams is untested.

\paragraph{No biological-fidelity claim.} Neuroscience supplies the bench's
testable mechanisms and metaphors --- replay, transfer, downscaling, generative
augmentation, TMR --- and nothing more. We do \emph{not} claim that Slow Wave
models the brain, that its operators are biologically faithful, or that any
result transfers to biology. The TMR comparison in particular is to a benchmark
effect size, via a prioritized-replay analogue, not a cued-reactivation protocol.
